A Spatial AR System for Wide-area Axis-aligned Augmentation of Planar Scenes in Industrial Settings

### 2021-07-05 paper/elsarticle/elsarticle-template.tex
Update elsarticle-template.tex

\paragraph{Projector calibration} As with camera calibration, projector calibration relies on 2D-3D correspondences, yet we obtain them in this case by projecting a pattern of circles. We rely on an algorithm to detect the circle pattern center points in the circles pattern image in the image plane of the projector \cite{bradski2000opencv}, giving the 2D positions of our 2D-3D correspondences (cf.\ Figure~\ref{fig:2d}(a)). We project the circles pattern image to each of the target locations, and use the camera to acquire a projector calibration image for each. Given a projector calibration image, we detect the circle centers of the \textit{projected} circles pattern (cf.\ Figure~\ref{fig:2d}(b)); given the scene plane (the recovery of which we shall turn to in the paragraph that follows) and such a 2D circle center $\mathbf{x}$, its 3D correspondence is obtained by intersecting the back-projection of $\mathbf{x}$ with the scene plane (cf.\ Figure~\ref{fig:3d}). Since the algorithm that yields 2D circle centers does so in a consistent ordering, we thus obtain the 2D-3D correspondences between the projector's image plane and the scene required for projector calibration, yielding the projector calibration matrix~$\mathtt{K}_\text{proj}$.

>>>>

\paragraph{Projector calibration} As with camera calibration, projector calibration relies on 2D-3D correspondences, yet we obtain them in this case by projecting a pattern of circles. We rely on an algorithm to detect the circle pattern center points in the circles pattern image in the image plane of the projector \cite{bradski2000opencv}, giving the 2D positions of our 2D-3D correspondences (cf.\ Figure~\ref{fig:2d}(a)). We project the circles pattern image to each of the target locations, and use the camera to acquire a projector calibration image for each. Given a projector calibration image, we detect the circle centers of the \textit{projected} circles pattern (cf.\ Figure~\ref{fig:2d}(b)); given the scene plane (the recovery of which we shall return to in the paragraph that follows) and such a 2D circle center $\mathbf{x}$, its 3D correspondence is obtained by intersecting the back-projection of $\mathbf{x}$ with the scene plane (cf.\ Figure~\ref{fig:3d}). Since the algorithm that yields 2D circle centers does so in a consistent ordering, we thus obtain the 2D-3D correspondences between the projector's image plane and the scene required for projector calibration, yielding the projector calibration matrix~$\mathtt{K}_\text{proj}$.
